Discovering Focused Microgenre Communities: Toy example

### 2023-08-02 07-new-micro-analysis-for-real.Rmd
Updated and new functions

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(haven)
    library(here)
    library(sjPlot)
    library(tidyverse)
    load(file= here("dat", "lclust-res.RData"))
```

@@

```{r}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    m <- genre.reg.mods("Country", k = 7,
                        xvars = c("educ", "race", "gender", "age.n",
                           "subjclass"))
    tab_model(m, digits = 3, show.ci = FALSE, 
              file = here("Tabs", "reg-tab-latin.html"))
```

```{r}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    latin.micro <- micro.genre.dat("Latin", k = 6)$all %>% 
      left_join(demog.dat())
    head(latin.micro)
    mod1 <- lm(as.numeric(Latin_1) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod2 <- lm(as.numeric(Latin_2) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod3 <- lm(as.numeric(Latin_3) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod4 <- lm(as.numeric(Latin_4) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod5 <- lm(as.numeric(Latin_5) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod6 <- lm(as.numeric(Latin_6) ~ educ + race + gender + age.n, 
               data = latin.micro)
    tab_model(mod1, mod2, mod3, mod4, mod5, mod6,
                show.ci = FALSE, auto.label = FALSE, digits = 3,
                #dv.labels = c(),
                #rm.terms = c(), 
                #pred.labels = c(), 
                file = here("Tabs", "reg-tab-latin.html") 
              )
    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-latin-ASR.png"))
```

>>>>

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(ggplot2)
    library(haven)
    library(here)
    library(sjPlot)
    library(tidyverse)
    load(file= here("dat", "lclust-res.RData"))
```

@@

```{r}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    a <- demog.dat()
    summary(a)
    spec <- c("educ", "parcoll", "age.n", "blk", "his", "asn", "gender")
    labs <- c("Intercept", "Education", "Parents College",
                            "Age", "Race ID: Black", "Race ID: Hispanic",
                            "Race ID: Asian", "Gender ID: Woman")

    res.latin <- genre.reg.mods("Latin", k = 4, xvars = spec)
    res.metal <- genre.reg.mods("Heavy_Metal", k = 4, xvars = spec)

    tab_model(res.latin$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-latin.html"))
    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
    tab_model(res.metal$mods, 
              digits = 3, show.ci = FALSE, 
              auto.label = FALSE, transform = NULL,
              pred.labels = labs,
              file = here("Tabs", "reg-tab-metal.html"))
    #webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
```

```{r}
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "plot.preds.R"))
    age.preds <- pred.probs(x = "age.n", res.latin$mods)
    p <- plot.preds(d = age.preds, 
                    xb = c(3, 7, 11),
                    xlabs = c("Young", "Mid. Aged", "Old"),
                    yl = .1, 
                    xm = 2, 
                    xl = 12)
    p
```
`
